\begin{rubric}{Courses and activities}
\subrubric{Neuroscience}

\entry*[February 2024] \textbf{fMRi Postpfrocessing Course: Resting State \& FSL}, Organized by the Center for Clinical Neuroscience. Hospital los Madroños. \textbf{Hours}: 12 hours.

\entry*[October 2021] \textbf{Hackathon Brain Code Games}, Organized by the Spanish Society of Neuroscience (SENC) and the Universidad Autónoma de Madrid (UAM). \textbf{Hours}: 60 hours.

\entry*[October 2020] \textbf{First Neutouch Summer School: Touch for Prosthetics}, Online. Organizer: Neutouch.

\entry*[April 2020] \textbf{BCI \& Neurotechnology Spring School 2020}, Online. Organizer: g.tec.


 \entry*[June 18, 2019] \textbf{Biological Risk (4h)}, Madrid. Organizer: Prevention of Risks Service, Universidad Autónoma de Madrid (UAM).

 \entry*[July 4, 2019] \textbf{Security on Chemicals Handling (4h)}, Madrid. Organizer: Prevention of Risks Service, Universidad Autónoma de Madrid (UAM).


\subrubric{Science disemination and interdisciplinarity}

\entry*[March, 2024 and 2025] \textbf{Organization and Conduction of course titled: "Free Software for Research Carreer"}, Universidad Autónoma de Madrid (UAM).

\entry*[January 25, 2023] \textbf{Conference "Open Science in the Spanish University and its Impact on Research Development and Evaluation"}, Interuniversity Institute INAECU.

\entry*[May 2021] \textbf{\#HiloTesis Dissemination Contest}, Organized by CRUE.

\entry*[October 2020 to February 2021] \textbf{Interdisciplinary Views in Scientific Research (5 ECTS)}, Madrid. Organizer: EDUAM, Universidad Autónoma de Madrid (UAM).

\entry*[February to June 2018] \textbf{Scientific Entertainer Course at Science Museum (100h; 4 ECTS)}, Granada. Organizer: Parque de las Ciencias; University of Granada (UGR).

\subrubric{Women in Science and STEM}
\entry*[June 2024] \textbf{AI Workshop for campus "I want to be an woman engineer"}, Universidad Autónoma de Madrid (UAM).

\entry*[February 2024] \textbf{Gender-Perspective Science Communication Course}, Science Culture Unit, Universidad Autónoma de Madrid (UAM).

\entry*[June 2022] \textbf{Participation in the Roundtable "Studying STEM"}, Project: "I Want to Be an Engineer - UAM", Organized by the School of Engineering. Universidad Autónoma de Madrid (UAM).

 \subrubric{Teacher training courses}

 \entry*[May 9–11, 2022] \textbf{Towards an Inclusive University: Transformative Elements}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: — \textbf{Hours}: 6.
 
 \entry*[February 15–17, 2023] \textbf{How to Evaluate Learning Outcomes}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 1 \textbf{Hours}: 8.
 
 \entry*[April 20–27, 2023] \textbf{Detection and Management of Psychological Issues Among Students}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 1 \textbf{Hours}: 8.
 
 \entry*[October 17–24, 2023] \textbf{The Concept of Competence and Competency-based Training}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 1 \textbf{Hours}: 8.
 
 \entry*[February 19–20, 2024] \textbf{Authority and Leadership Course}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 1 \textbf{Hours}: 8.
 
 \entry*[May–June 20–10, 2024] \textbf{Design and Planning of the Teaching-Learning Process in the Context of a Course. Preparation of the Course Syllabus}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 2 \textbf{Hours}: 16.
 
 \entry*[October 18–25, 2024] \textbf{Gamification and Game-based Learning: A Practical Workshop for Creating Educational Video Games}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 1 \textbf{Hours}: 8.
 
 \entry*[October 10–23, 2024] \textbf{Flipping the Classroom: An Introduction to the Flipped Classroom}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 1 \textbf{Hours}: 8.
 
 \entry*[May 26–29, 2025] \textbf{Evaluating Learning}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 1 \textbf{Hours}: 12.
 
 \entry*[May–June 13–04, 2025] \textbf{Creating a Dynamic Classroom}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 1 \textbf{Hours}: 12.
 
 \entry*[October 10, 2025] \textbf{Workshop “Teaching Blindly” (Fourth Edition)}, Faculty of Psychology, Universidad Autónoma de Madrid (UAM). \textbf{Event:} Accessible Psychology: “Without Groping in the Dark.”  \textbf{Hours}: 2.
 
 
\entry*[October-November 24-7] \textbf{Online Teaching and Intellectual Property: Practical Aspects for University Faculty}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 1 \textbf{Hours}: 9.

\entry*[November 4-11] \textbf{Motivation and University Learning}, Teacher Training Program. Universidad Autónoma de Madrid (UAM). \textbf{Credits}: 1 \textbf{Hours}: 8.

\subrubric{Other courses}
 \entry*[February 2021 - June 2021] \textbf{Organization and Participation in Research Group Seminars}, Organized by GNB.

\entry*[June 2023] \textbf{Participation in the Poster Exhibition at the Doctoral Week 2023}, Organized by the Graduate School. UAM.

\entry*[September 2023] \textbf{Attendance at the International Congress IBRO}, Organized by the International Brain Research Organization.

\entry*[Academic Period 2017/2018] \textbf{University of Granada Library: Formative Actions (3 ETCS)}, Granada. Organizer: University of Granada (UGR).

\end{rubric}